COG-ED Manuscript

### 2022-02-17 06_Paper/COG-ED/Manuscript.Rmd
added r squared to supplement

@@

>>>>

The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2b_r2, digits = 2)`.

@@

The conditional $R^2$ of the model describes the proportion of variance explained by both fixed and random effects, and is $R^2=$ `r format(h2c_r2, digits = 2)`.
